Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-04-01 doc/PRF2022/Reviews/ResponseToReviewer1.tex

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~C\'ecile Cottin-Bizonne,
\\ \\
\noindent 
We thank the Reviewer for their constructive feedback.
A point-by-point list of changes to the manuscript 
addressing the Reviewer's comments appears below.\\

\noindent As a summary, we have undertaken a major revision of the manuscript
that includes further detailed simulation data and analyses,
reorganized figures, and a new ``Results and Discussion'' section
written from scratch.  These changes address all the Reviewer's
comments and we believe the result is a significantly stronger manuscript.
\\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei Fu, Rolf Ryham, Bryan Quaife, and Yuan-Nan Young

\section*{Response to Reviewer 1}

\noindent Changes appear in \textcolor{red}{red}.
(Other changes specific to Reviewer 2 appear in \textcolor{magenta}{magenta}.)\\ \\

\noindent
\comment{The manuscript discusses the self-assembly of amphiphilic Janus
particles and their dynamics in various flow conditions. Different
morphologies are recovered for different boundary conditions which are
developed by varying the hydrophobicity on Janus particle surface.
These various boundary conditions give rise to unilamellar,
multilamellar and striated structures. Finally, these structures are
subjected to linear shear flow and Taylor-Green flow. The subject of
study is interesting to soft matter community.}

\begin{itemize}
  \item {\bf Response to Summary}: We thank the Reviewer for their
    positive assessment of our manuscript.  
%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}
\end{itemize}

@@

\noindent
\comment{My main criticism is the following: 1. Unilamellar,
multilamellar and striated structured are subjected to various flow
conditions, with increasing shear rate or strength of the flow (for TG
case). For all structures in both flows, the main result is that these
structures break eventually either for increased shear rate or increased
flow rate. But this is expected. What do all these results mean? I feel
that a constructive message is missing.}

\begin{itemize}
  \item[] {\bf Response:}
      The Results Section V of our first submission
    analyzed simulation data on a case-by-case basis. 
    This made it unnecessarily difficult for the reader to
    make meaningful connections and we agree with the Reviewer:
    a constructive message was missing.  Moreover,
    the large-shear-rate 
    simulation runs for the most part corresponded to breakage in
    JP phases.

    To address these deficiencies,
    we performed further simulations 
    for moderate shear rates ranging
    from $0$ ns$^{-1}$ to $0.1$ ns$^{-1}$ in shear flow
    and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$ in TG flow.
    These additional data allowed us to examine 
    material properties in greater detail: the new
    \begin{itemize}
      \item[$\bullet$] Figure 3 summarizes the strain and alignment data
        under \emph{all} flow and JP-type conditions.
      \item[$\bullet$] Figure 4 characterizes the change in free and binding energies.
      \item[$\bullet$] Figure 5 plots pre-rupture
        shear stress against shear rate revealing the rheological properties of
        the three distinct JP phases.    
    \end{itemize}
    A constructive message---identification a critical shear rate,
    relative binding strengths as a function of JP type,
    and effective viscosities and presence of shear thinning---is
    now formulated thanks to exploring the full range of
    shear rates.

    Finally, we normalized the TG flow rate (previously $V_0$)
    so that we can compare the shear and TG flow in terms of the same
    shear rate $\dot \gamma$.  See page 11, equation (24) and page 12,
    top paragraph.
\end{itemize}

\noindent
\comment{2. And the discussion section is not written well. Please write it
properly.}
    \begin{itemize}
    \item[] {\bf Response:}
      The address this,
      we rewrote the Results section from scratch
    to what is now Section V ``Results and Discussion''.
    We highlighted the section heading on page 11 to indicate
    that the entire section is rewritten.

    Starting on page 11, this section introduces the background flows,
    characterizes the system's capillary and P\'eclet numbers.
    As described in the previous response, Section V examines the data
    as a whole and is divided into subsections A. Strain and alignment,
    B. Free energy, and C. Rheology.

    The raw data, which was previously shown in the
    main text, has now been placed in Supplementary Material
    and appropriately captioned.  We also combined
    Figures 2 and 3 into a simpler, more readable Figure 2.

    Finally, we rewrote the previous Discussion Section VI from scratch
    into Section V, subsection D. Here,
    we perform a dimensional analysis of the critical shear rate $\dot \gamma_*$
    for rupture, show how fluid-structure interactions
    give rise to non-monotonic dependence, justify why
    fluctuation can been omitted from the simulations, and
    discuss the rheological data in the context of 
    rheologies for classical and active suspensions.

    We feel that these changes have significantly improved the readability
    of the manuscript.  As an added advantage, the main text of the
    revised manuscript is 21 pages, whereas the first submission's was
    25 pages.  
    \end{itemize}

@@

\noindent
\comment{Minor comments: 1. Page 18: The section ends with 
the statement “In previous work, Fu
et al. [18] determined the permeability constant of particle-based
vesicles in the context of shear background flow [53, 54]. “. I find
the statement abrupt and not related to the earlier text.}

\begin{itemize}
  \item[] {\bf Response:}
    We have omitted this sentence and rewritten the discussion
    for vesicles in TG flow.  See second middle of page 18.   
\end{itemize}

@@

\noindent
\comment{2. Fig. 8: Please describe what the arrows mean in (a), (b), (c) and
(d).}

\begin{itemize}
\item[] {\bf Response:}
  In our first submission, these arrows showed the clockwise or counterclockwise
  vesicle motion in TG flow.  These arrows have been omitted in the new Figure 6,
  and the motion is instead described in the middle of page 18. 
\end{itemize}

### 2023-04-01 doc/PRF2022/Reviews/ResponseToReviewer2.tex

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent Dear Prof. C\'ecile Cottin-Bizonne,\\

\noindent 
We thank the Reviewer for their constructive feedback.
A point-by-point list of changes to the manuscript 
addressing the Reviewer's comments appears below.\\

\noindent As a summary, we have undertaken a major revision of the manuscript
that includes further detailed simulation data and analyses,
reorganized figures, and a new ``Results and Discussion'' section
written from scratch.  These changes address all the Reviewer's
comments and we believe the result is a
significantly stronger manuscript.\\

@@

\noindent
Sincerely,
\\
\noindent
Szu-Pei Fu, Rolf Ryham, Bryan Quaife, and Yuan-Nan Young

\section*{Response to Reviewer 2}

\noindent Changes appear in \textcolor{magenta}{magenta}.
(Other changes specific to Reviewer 1 appear in \textcolor{red}{red}.)\\ \\

@@

\begin{itemize}
  \item {\bf Response}: We thank the Reviewer for this positive appraisal of 
our manuscript. 
\end{itemize}

%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}

\noindent
\comment{1) The authors study the nano-hydrodynamics around the JPs very carefully by
modeling the flow as a continuous 2D Stokes flow. While I understand that
modeling the dynamics in 2D instead of 3D is fair, i.e. their results should in
principle be extensible to 3D, my major concern is the absence of thermal
fluctuations. They are expected to be very relevant on the nanometer scale,
regarding self-assembly, dynamics and stability of the JP structures.
}

\begin{itemize}
\item {\bf Response:}
  To justify excluding thermal fluctuations in our system,
  the new Section V D 
  analyzes the fluctuation Fourier spectrum 
  of a planar membrane corresponding to the Type I JP bilayer phase
  (starting on page 18).
  As the Reviewer points out, our 2D system applies
  to a transversely invariant bilayer with depth denoted by $L_y$.
  Equation (29) shows that the expected fluctutation is small
  relative to particle size, meaning that thermal fluctuations can
  be safely ignored when the 2D system corresponds to a material that 
  is more than a few particles deep.  The elastic modulus $\kappa$ for
  Type II and Type III phases is still greater than for Type I.

  We point out though, that because the wave vector $\mathbf{k}$ is inversely
  proportional to the characteristic phase-sample size,
  fluctuation will be large provided $L_x$ or $L_y$ is sufficiently large,
  as in the case of micron-sized vesicles.
\end{itemize}

@@

\noindent
\comment{2) The shear rates studied are below nanoseconds$^{-1}$. What is the relevance of
such small shear rates in real (biological) systems? Furthermore, in presence of
noise, I would expect that the JP diffusive timescale is much smaller then the
shear flow time scale, and hence effectively the associated Peclet number, i.e.
importance of flow compared to noise, is negligible in this system?

Before I can recommend publication, the authors should clarify these points, in
particular justify why noise can be neglected, and why such small shear rates
are relevant.}

\begin{itemize}
\item {\bf Response:}
  In the beginning  of the new Section V ``Results and Discussion'' (page 12),
  we now derive the range of shear rates 
  based on the capillary number $\mathrm{Ca}$.  The derivation shows that shear forces dominate
  interfacial forces when $\dot \gamma$ exceeds
  10$^{-2}$ ns $^{-1} = 10^6$ s$^{-1}$.  Following the derivation,
  we include references to molecular dynamics simulations that also
  consider nm system-sizes like ours, along with references to
  larger experimental systems were shear rates are more moderate,
  on the order of $10^3$ s$^{-1}$.  We end by calculating the
  P\'eclet number $\mathrm{Pe} = 60$, showing that
  noise is negligible compared to advection in our system.

  Although the range of simulation shear rates is unchanged in our
  revision, we thank the Reviewer for pointing these details out
  as their comment has clarified
  two important points: why we chose the range of shear
  rates that we did and how neglecting noise and
  thermal fluctuation can be justified in our system.

### 2023-04-01 doc/PRF2022/PRF_main.tex
Responses and Letter done:

%%%%%%%

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $\pi \lambda \times \pi
\lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

In both cases, $\dot \gamma$ is the shear rate. The flow rate $\lambda
\dot \gamma$ is chosen so that~\eqref{eq:tg_flow} has the same rate of
viscous dissipation per area as for~\eqref{eq:sh_flow}. In other words,
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ is the
same for $\uu = \uu_{\infty}^{\text{sh}}$ as for $\uu =
\uu_{\infty}^{\text{TG}}$ when integrated over a TG cell $A$.

{\color{magenta}
To obtain a range for $\dot \gamma$, consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$~nm and $\kappa = 20\;\kbt$ are the characteristic phase
sample radius and bending rigidity, respectively. That is, $\kappa$
gives the elastic stress for restoring the phase-sample shape. Shear
stress overcomes elastic stress when $C_a > 1$ and this yields $\dot
\gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s$^{-1}$. Thus our values
for $\dot \gamma$ range between $0$ ns$^{-1}$ corresponding to quiescent
flow up to $0.2$~ns$^{-1}$ capable of rupturing the sample. Such shear
rates are compatible with molecular dynamics simulation
\cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA}, and shearing in blood capillary
vessels \cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.
From the particle diffusion time $D/L^2$  
and advection time $L/u = (\dot\gamma)^{-1}$,
$D = 0.17\cdot 10^{-9}$~m$^2$~s$^{-1}$ and $L \sim 10$~nm, we 
obtain a P\'eclet number $\mathrm{Pe} = (D/L^2)/(L/u) \sim 60$,
suggesting that advection dominates the particle transport.
% L u = L^2 gammadot = 10 nm^2/ns 
% D = kBT/(6 pi mu c) = kBT/(6 pi mPa s c) 
%   = kBT/(6 pi 1e-3 N/m^2 1.25 nm) 
%   = 4 1e-12 N nm/(6 pi 1.25e-3 m^{-2} s N nm) 
%   = 0.17e-9 m^2/s
%  
% Pe = L u/D = 10 nm^2/ns/(0.17e-9 m^2/s)
%    = 59e9 1e-18 1e9 = 59
}

@@

For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
JP vesicle as the inner leaflet of JPs move clockwise along the boundary
faster than the outer leaflet. For $\lambda=3$~nm and $\lambda=4$~nm,
there is only one TG cell inside the JP vesicle and the JPs in the
bilayer tank-tread in the counter-clockwise direction (Figure
\ref{fig:PramChange}(b)--(e)). 
%
Finally, we calculated the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area achieves a
steady state $A_{\infty}/A_0$ that is greatest for $\lambda = 4$~nm yet least for
$\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (data not shown). 
In other words, the fluid-structure interactions of JPs give rise to 
non-monotonic dependence of membrane permeability on the TG cell size $\lambda$.
Such dynamic permeability due to fluid-structure interactions is also found in the clogging of
spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.

>>>>

%%%%%%%
{\color{red}
\section{Results and Discussion}}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
{\color{red}
  \begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
  \end{equation}
  }
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $\pi \lambda \times \pi
\lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

{\color{red}
  In both cases, $\dot \gamma$ is the shear rate. The flow rate $\lambda
\dot \gamma$ is chosen so that~\eqref{eq:tg_flow} has the same rate of
viscous dissipation per area as for~\eqref{eq:sh_flow}. In other words,
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ is the
same for $\uu = \uu_{\infty}^{\text{sh}}$ as for $\uu =
\uu_{\infty}^{\text{TG}}$ when integrated over a TG cell $A$. 
}

{\color{magenta}
To obtain a range for $\dot \gamma$, consider the capillary number 
\begin{equation}
\label{eq:capillary}
\mathrm{Ca} = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$~nm and $\kappa = 20\;\kbt$ are the characteristic phase
sample radius and bending rigidity, respectively. That is, $\kappa$
gives the elastic stress for restoring the phase-sample shape. Shear
stress overcomes elastic stress when $\mathrm{Ca} > 1$ and this yields $\dot
\gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s$^{-1}$. Thus our values
for $\dot \gamma$ range between $0$ ns$^{-1}$ corresponding to quiescent
flow up to $0.2$~ns$^{-1}$ capable of rupturing the sample. Such shear
rates are compatible with molecular dynamics simulation
\cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA}, and shearing in blood capillary
vessels \cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.
From the particle diffusion time $D/L^2$  
and advection time $L/u = (\dot\gamma)^{-1}$,
$D = 0.17\cdot 10^{-9}$~m$^2$~s$^{-1}$ and $L \sim 10$~nm, we 
obtain a P\'eclet number $\mathrm{Pe} = (D/L^2)/(L/u) \sim 60$,
suggesting that advection dominates the particle transport.
% L u = L^2 gammadot = 10 nm^2/ns 
% D = kBT/(6 pi mu c) = kBT/(6 pi mPa s c) 
%   = kBT/(6 pi 1e-3 N/m^2 1.25 nm) 
%   = 4 1e-12 N nm/(6 pi 1.25e-3 m^{-2} s N nm) 
%   = 0.17e-9 m^2/s
%  
% Pe = L u/D = 10 nm^2/ns/(0.17e-9 m^2/s)
%    = 59e9 1e-18 1e9 = 59
}

@@

{\color{red} For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
JP vesicle as the inner leaflet of JPs move clockwise along the boundary
faster than the outer leaflet. For $\lambda=3$~nm and $\lambda=4$~nm,
there is only one TG cell inside the JP vesicle and the JPs in the
bilayer tank-tread in the counter-clockwise direction (Figure
\ref{fig:PramChange}(b)--(e)). }
%
Finally, we calculated the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area achieves a
steady state $A_{\infty}/A_0$ that is greatest for $\lambda = 4$~nm yet least for
$\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (data not shown). 
In other words, the fluid-structure interactions of JPs give rise to 
non-monotonic dependence of membrane permeability on the TG cell size $\lambda$.
{\color{red}Such dynamic permeability due to fluid-structure interactions is also found in the clogging of
spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.}
